\pagebreak
\settowidth{\versewidth}{Your houses they pull down to fright poor men in town,}
\poemtitle{The Diggers' Song}
\begin{verse}[\versewidth]

You noble Diggers all, stand up now, stand up now,\\
You noble Diggers all, stand up now,\\
The waste land to maintain, seeing Cavaliers by name\\
Your digging do distain and your persons all defame\\
Stand up now, Diggers all.

Your houses they pull down, stand up now, stand up now,\\
Your houses they pull down, stand up now.\\
Your houses they pull down to fright poor men in town,\\
But the gentry must come down and the poor shall wear the crown.\\
Stand up now, Diggers all.

With spades and hoes and ploughs, stand up now\dots{}\\
Your freedom to uphold, seeing Cavaliers are bold\\
To kill you if they could and rights from you withhold.

Their self-will is their law, stand up now\dots{}\\
Since tyranny came in they count it now no sin\\
To make a gaol a gin and to serve poor men therein.

The gentry are all round, stand up now\dots{}\\
The gentry are all round, on each side they are found,\\
Their wisdom's so profound to cheat us of the ground.

The lawyers they conjoin, stand up now\dots{}\\
To arrest you they advise, such fury they devise,\\
But the devil in them lies, and hath blinded both their eyes.

The clergy they come in, stand up now\dots{}\\
The clergy they come in and say it is a sin\\
That we should now begin our freedom for to win.

'Gainst lawyers and 'gainst priests, stand up now, stand up now,\\
'Gainst lawyers and 'gainst Priests, stand up now.\\
For tyrants are they both even flat against their oath,\\
To grant us they are loath free meat and drink and cloth.\\
Stand up now, Diggers all!
\end{verse}
