%\pagebreak
\settowidth{\versewidth}{}
\poemtitle{Shepherds Rejoice}
%\begin{multicols}{2}
\begin{lilypond}[staffsize=16]
\version "2.18.2"

global = {\key f \major \time 4/4 \numericTimeSignature }
\new ChoirStaff
<<
  \new Staff
  <<
    \global
    \relative c''
      {\sacredHarpHeads \partial 2
      \repeat volta 2 {
      c2 | c4 a a c | f f d c | c d c c
      c2 }
      f2 | f4 a c, c | d f f d | c c d f | f2\fermata
      c | d4 f f c | f, f c' c | c d c c | c1 \bar ".."}


    \addlyrics {
    \set stanza = #"1. "
    Shep -- herds, re -- joice! lift up your eyes,
    And send your fears a -- way
    Je -- sus, the God whom an -- gels fear,
    Comes down to dwell with you.
    To -- day He makes His en -- trance here,
    But not as mon -- archs do.
    }
    \addlyrics {News from the re -- gions of the skies,
    A Sav -- ior's born to -- day.}
  >>

  \new Staff
  <<
    \global
    \relative c''
    { \sacredHarpHeads \partial 2
    \repeat volta 2 { a2 | f4 f f f | a a f a | f f g g |
    a2}
    a2 | a4 f a g | f f a g | a a f a | a2\fermata
    a | g4 a a f | a a f a | f f g g | a1 \bar ".."
    }
    \addlyrics {
    \set stanza = #"2. "
    No gold nor pur -- ple swad -- dling bands,
    Nor roy -- al shin -- ing things,
    Go, shep -- herd, where the in -- fant lies,
    And see His hum -- ble throne;
    The tears of joy in all your eyes,
    Go, shep -- herd, kiss the Son.
    }
    \addlyrics {A man -- ger for His cra -- dle stands,
    And holds the King of Kings.}

  >>

  \new Staff
  <<
    \global
    \relative c'
    {
    \sacredHarpHeads \partial 2
    \repeat volta 2{ f2 | a4 c c a | c c a f | a a g g |
    f2}
    c'2 | c4 d f g | a d, c d | f f d c | c2\fermata
    f | d4 c c a | c c a f | a a g g | f1 \bar ".."
    }
    \addlyrics {
    \set stanza = #"3. "
    Thus Ga -- briel sang and straight a -- bound
    The heav'n -- ly ar -- mies throng

    Glo -- ry to God who reigns a -- bove,
    Let peace sur --round the earth.
    Mor -- tals shall know their Mak -- er's love
    At their Re -- deem -- er's birth.
    }
    \addlyrics {They tune their harps to soft -- ly sound,
    And thus con -- clude their  song.}
  >>

  \new Staff
    <<
    \global
    \relative c
    {\clef "bass"
    \sacredHarpHeads \partial 2
    \repeat volta 2{ f2 | f4 f f c | f f d c |f f c c |
     f2}
    f2 | f4 a f c' | a a f d  | f f d c | f2\fermata
    f | d4 f f f | c c f c  | f f c c | f1 \bar ".."
    }
    >>
  >>
\end{lilypond}