\documentclass[12pt]{article}
\usepackage[a4paper,inner=3.5cm,outer=3.5cm,bottom=4cm,top=3cm]{geometry}
\usepackage[]{verse,enumitem}
\usepackage{graphicx}
\usepackage{multicol}
\newcommand*{\dotsize}{10}
\date{}




\begin{document}
\title{Bells of Caroldise}
\maketitle
\tableofcontents
\newcommand{\attrib}[1]{%
\nopagebreak{\raggedleft\footnotesize #1\par}}
\renewcommand{\poemtoc}{section}

\makeatletter		%%This hack changes \input to point to /Songs.
%\def\input@path{{./Songs/}}	
%or: \def\input@path{{/path/to/folder}{/path/to/other/folder}}
\makeatother

\newenvironment{chorus}[1][]{%
	\itshape  
  	\begin{itemize}[label={},leftmargin=-\vgap]
    \item}
    {\end{itemize}}
\pagebreak

%\pagebreak
\settowidth{\versewidth}{When a bold set of ruffians they entered our cave,}
\poemtitle{All Things Are Quite Silent}
%\begin{multicols}{2}

\begin[staffsize=\dotsize]{lilypond}
\
\relative c' {
\time 3/4
\partial 4
a'8( g) | f4 e d | g a b | g a8( g) e4 |d2
d8( e) | f4 e d | g( a) b | g a8( g) e4| d2
a'8 c | b([ a]) g( a) b4 | c8( b) a4 a | d c d | a2
a8 g | f4 e d | g a b | g a8( g) e4 | d2 ||
}
\addlyrics {
    All | things are quite | si -- lent each | mor -- tal__ at | rest, When | me and my | love __ got snug in __ one nest, When a | bold set of | ruf -- fians they | en -- tered our | cave, And they | forced my dear | jew -- el to | plough the salt | wave.
  }
\end{lilypond}

\begin{verse}[\versewidth]
All things are quite silent, each mortal at rest,\\
When me and my love got snug in one nest,\\
When a bold set of ruffians they entered our cave,\\
And they forced my dear jewel to plough the salt wave.

I begged hard for my sailor as though I begged for life.\\
They'd not listen to me although a fond wife,\\
Saying: `The king he wants sailors, to the sea he must go'\\
And they've left me lamenting in sorrow and woe

Through green fields and meadows we ofttimes did walk,\\
And sweet conversation of love we have talked,\\
With the birds in the woodland so sweetly did sing,\\
And the lovely thrushes' voices made the valleys to ring

Although my love's gone I will not be cast down,\\
Who knows but my sailor may once more return?\\
And will make me amends for all trouble and strife,\\
And my true love and I might live happy for life.
\end{verse}
%\end{multicols}

%\pagebreak
\settowidth{\versewidth}{Down in the meadows forth to plough;}
\poemtitle{On Christmas Day}

\begin[staffsize=\dotsize]{lilypond}
\
\relative c' {
\time 5/4
\key g \minor
\partial 4
d4 | g( a) bes c a | g8([ a]) g([ f]) d2
d'4 | d c a( g) f | g a8( c) bes2 c4 |
\time 6/4
d4.( ees8) d([ c]) bes4( c) d8( ees) | d4 bes a2. c8.( bes16) |
\time 5/4 g8( f) d4 f( g) a8 c | c4 bes g
 }
\addlyrics {On Christ -- mas Day it hap -- pened so,
Down in the mead -- ows forth to __ plough;
As we __ were plough -- ing on so fast,
Up comes sweet Je -- sus his -- self at last. 
      }
\end{lilypond}

\begin{verse}[\versewidth]
On Christmas day it happened so,\\
Down in the meadows forth to plough;\\
As we were ploughing on so fast,\\
Up comes sweet Jesus his self at last.

`O man, O man, what makes you plough\\
So hard upon the Lord's birthday?'\\
The farmer answered him with great speed:\\
`For to plough this day we have great need'.

His arms did quaver to and fro;\\
His arms did quaver, he could not plough.\\
The ground did open and lose him in,\\
Before he could repent of sin.

His wife and children are out of place,\\
His beasts and cattle they die away;\\
His beasts and cattle they die away,\\
For the breaking of our Lord's birthday.
\end{verse}



\end{document}